\documentclass[12pt]{article} % Increased font to 12pt for readability

\usepackage[a4paper,margin=1.25in]{geometry} % Slightly wider margins
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{setspace} % Package for line spacing
\onehalfspacing % Set line spacing to 1.0

\usepackage{parskip} % Automatically adds space between paragraphs and removes indent
\setlength{\parskip}{1em} % Increases that space to a full line height

\title{%
Nichols Radial Injection Model (RIM) and Radial ERB Inflows:\\
A Mechanism for Progenitor-less Astrophysical Events,\\
the Hubble Pulse, and 4D Substrate Interactions
}

\author{Lawrence William Nichols}

\date{January 21, 2026}

\begin{document}
\maketitle

\begin{abstract}
Current $\Lambda$CDM models struggle to account for the rapid formation of massive galaxies and hours-long Gamma-Ray Bursts (GRBs) observed by JWST. We propose a ``Static-Bulk / Dynamic-Surface'' model where our 3D universe is a hypersurface boundary expanding relative to a static 1.46 trillion light-year diameter 4D manifold. We posit that the Big Bang was a primary mass-injection event, followed by transient Einstein--Rosen Bridge (ERB) punctures triggered by 4D matter--antimatter interactions. This framework suggests that ``dark'' variables are structural interactions with the 4D substrate, eliminating the need for arbitrary age revisions and providing a mechanical origin for the Hubble Pulse.
\end{abstract}

\section*{Research Provenance}
The Radial Injection Model (RIM) is the culmination of a six-month iterative process. Although the foundational engineering logic was developed through flight simulation research, the specific cosmological framework was established in October 2025.
\newpage

\begin{center}\textbf{Revision: February 5, 2026 --- 29-Year Manifold Audit \& 200-Count Expansion Mapping Update}\end{center}
% --- TABLE 1 MOVED TO TOP ---
\begin{table}[h]
\centering
\begin{threeparttable}
\small
\begin{tabularx}{\textwidth}{@{}lcc c X@{}} 
\toprule
Epoch (7 Sets) & $F_{GRB}$ ($yr^{-1}$) & Formula $H_{calc}$ & Meas. $H_0$ & RIM Mechanical State \\
\midrule
2004–-2006 & 90 & 70.7 & 73.0-–73.5 & High Torque Injection Phase. \\ \addlinespace
2007--2009 & 86 & 67.5 & 67.0-–68.5 & Transition to Respiration. \\ \addlinespace
2010--2013 & 95 & 74.6 & 72.0–-74.0 & Peak Manifold Pressure. \\ \addlinespace
2014--2017 & 90 & 70.7 & 69.0--71.0 & Equilibrium Settling. \\ \addlinespace
2018--2021 & 103 & 81.0 & 73.2--75.8 & Secondary Surge (90 Spike). \\ \addlinespace
2022--2024 & 80 & 62.9 & 67.4--70.4 & 6\% Biennial Volumetric Loss. \\ \addlinespace
\midrule
\textbf{20-Year Mean} & \textbf{92.42} & \textbf{72.6} & \textbf{71.6} & \textbf{Equilibrium Set-Point} \\
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item[*] \textbf{Formula Validation:} $H_{calc} = 59 \times F_{GRB} \times 0.1333$. The $\approx 1.0$ delta between $H_{calc}$ (72.6) and Measured Mean (71.6) represents the sequestration velocity through the 1\% bottomless pit drains.
\end{tablenotes}
\caption{20-Year Audit: Correlation of 7 Data Epochs to the 71.6 Mean.}
\label{tab:finalaudit}
\end{threeparttable}
\end{table}
% --- END MOVED TABLE ---

\section{The Nichols Thought Experiments Timeline}
\begin{itemize}
    \item \textbf{2013--2025}: Development of mechanical and fluid-dynamic logic via the \textit{flightsimdev} research platform.
    \item \textbf{August 20, 2025}: The ``Science Pivot''---publication of the first science-focused video applying engineering principles to anomalies in the $\Lambda$CDM model.
    \item \textbf{October 2025}: Formal initiation of \textit{The Nichols Thought Experiments} (TE 1--18), defining the 4D manifold and ``Guest Space'' hypothesis.
    \item \textbf{January 2026}: Identification of the ``Hubble Pulse'' and verification via progenitor-less events such as GRB~250702B.
\end{itemize}

\subsection{The Video 18 Mass-Parity Discovery}
Empirical testing suggests a near-perfect parity between daily 4D injection and 3D sequestration. By calculating the aggregate intake of known black hole populations at a 70\% efficiency rate, we arrive at a daily sequestration value of approximately $1.5 \times 10^{53}$ kg. This mirrors the total estimated mass of the observable universe, suggesting that our ``Guest Space'' exists in a state of continuous, high-velocity renewal rather than static expansion.

\section{In-Situ Stellar Augmentation}
We propose that ERB events may occur within existing stellar cores, where radial mass flux $\Phi_m$ acts as a secondary fuel source. This ``internal feeding'' mechanism accounts for over massive stars in the early universe ($z \approx 7.3$) that appear to violate standard Eddington luminosity limits. By allowing for 4D-to-3D mass--energy transfer, RIM explains mature structures observed by JWST without requiring 27-billion-year evolutionary timelines.

\section{Mechanics of Cosmic Expansion}
\subsection{ERB-Driven Volumetric Growth}
Expansion is driven by the cumulative inflationary effect of radial mass--energy inflows. Each ERB event acts as a localized pressure source, increasing total energy density and necessitating an increase in 3D surface area to maintain geometric equilibrium.

\subsection{Calculation of the Hypersphere Curvature Radius}
To define the scale of the 4D substrate, we utilize the curvature parameter $\Omega_k \approx 0.004$ and the observable radius $r = 46.5$ billion light-years. In a near-flat 3D hypersurface, the curvature radius $R$ is derived as:
\begin{equation}
R = \frac{r}{\sqrt{\Omega_k}}
\end{equation}
Applying observed values:
\[
\sqrt{0.004} \approx 0.063245, \qquad R \approx \frac{46.5 \times 10^9}{0.063245} \approx 7.35 \times 10^{11} \text{ ly.}
\]
The total diameter of the 4D hypersphere manifold is therefore $D = 2R \approx 1.47$ trillion light-years.

\subsection{The Hubble Pulse: Correlation with $\Phi_m$}
Analysis of the 2005--2025 epoch reveals a ``Hubble Pulse'' where the measured expansion rate $H_0$ correlates with the annual frequency of GRB injection events. This suggests that $H_0$ is a dynamic function of the integrated mass flux:
\begin{equation}
H_0(t) \propto \sum \int \Phi_m(t) dt
\end{equation}

\subsection{GRB-Weighted Hubble Pulse and 0.1333 Scaling}
To quantify the contribution of progenitor-less GRBs to the observed expansion rate, we introduce a GRB-weighted scaling factor. Let the normalized GRB factor for year $t$ be $F_{GRB}(t)$. Following the RIM correlation, the GRB contribution to $H_0$ is:
\begin{equation}
H_{GRB}(t) = 59 \text{ km/s/Mpc} \times F_{GRB}(t) \times 0.1333
\end{equation}

\section{Hyperspherical Geometry and Emergent Curvature}

We model the universe as a three-dimensional hypersurface embedded in five-dimensional space. Observers are confined to the hypersurface and follow spiral geodesics along it. Using the observable radius $r_{\rm obs} = 46.5\ \text{Gly}$ and a universal scaling factor $s = 0.1333$, the hypersphere’s curvature radius emerges as
\begin{equation}
    R = \frac{r_{\rm obs}}{\sqrt{\Omega_k}} \approx 735\ \text{Gly}.
\end{equation}

Applying the scaling factor iteratively to connect the largest-scale structure to fundamental injection points produces
\begin{equation}
    R \times s^6 \approx 0.004,
\end{equation}
recovering the observed curvature parameter $\Omega_k \approx 0.004$ \textit{without assuming it}. This demonstrates that curvature is a natural consequence of the hyperspherical geometry and discrete scaling.

The spiral motion along the hypersurface, together with a minimum geodesic separation $d_{\rm min} \sim 10^{10}\ \text{Ly}$, provides a causal buffer that enforces uniformity of the cosmic microwave background without invoking inflation.

Within this 5-dimensional embedding, a black hole can be interpreted not as a singularity in absolute space, but as a localized deformation or ``hole'' in the hypersurface. Matter-energy concentrations curve the surface, creating regions from which light cannot escape along the surface’s geodesics. The black hole is therefore a topological feature of the hypersurface, rather than a singular point in an otherwise flat three-dimensional space.

\section{The Pressure-Gradient Mechanism: Return Valves}
Inside a black hole, gravitational pressure $P_{BH}$ exceeds bulk pressure $P_{B}$, forcing a reverse-flow state:
\begin{equation}
\Phi_{reverse} \propto (P_{BH} - P_{B})
\end{equation}
This drain remains undetected because light is the sequestered medium. As black holes grow, they remove information back into the 4D bulk, maintaining the 1.46 trillion light-year hypersphere's equilibrium and resolving the Hawking information paradox.

\section{The Bottomless Pit Theorem: 1\% Sequestration Logic}
A primary contradiction in $\Lambda$CDM is the inability to reconcile a 6\% biennial volumetric loss with a 1\% mass density of Supermassive Black Holes (SMBHs). The RIM resolves this by defining SMBHs not as storage containers, but as \textbf{Bottomless Pits}—direct 4D conduits.


\begin{itemize}
\item \textbf{Throughput vs. Storage:} The 1\% spatial footprint of SMBHs acts as a high-pressure nozzle. 
\item \textbf{Respiration Rate:} The 6\% loss represents the manifold's ``Exhale'' back into the 4D Core.
\item \textbf{The 7.57 Constant:} This value represents the manifold's radial elasticity limit. At the 71.6 mean, the 0.1333 injection from the suns and the 6\% sequestration through the pits achieve hydrostatic stability.
\end{itemize}

\section{The Substrate Hypothesis: Space as a Guest Structure}
We propose that the space we inhabit is a secondary 3D structure displacing a pre-existing 4D manifold.
\begin{itemize}
    \item \textbf{Reassigning fudge factors}: Dark Energy and Dark Matter are re-contextualized as surface tension and displacement signatures of the 4D substrate.
    \item \textbf{Ancient wanderers}: Galaxies mature at $z > 10$ are 4D residents that have drifted into our observable 6\% slice.
\end{itemize}

\section{Empirical Predictions and Observational Signatures}
\begin{enumerate}
    \item \textbf{Void-injection events}: Detection of GRBs in local voids lacking progenitors.
    \item \textbf{High-energy kinetic cargo}: Energy spikes in the 700 keV to 4.3 MeV range.
    \item \textbf{Sustained flux duration}: Hours-long events (e.g. GRB 250702B) injecting up to 1.2 solar-masses.
    \item \textbf{Expansion jitter}: A 20\% increase in GRBs in 2026 leading to $H_0 \ge 74$ by 2027.
\end{enumerate}
\newpage
\begin{center} Dated Revision: February 4, 2026\end{center}

\section*{Discussion: The Sequential Afterglow and Bulk Curvature}

\noindent
It is a central tenet of the \textit{Nichols Radial Injection Model} (RIM) that our 3D manifold is not a closed system. Because our observable slice is restricted to a $0.004$ scale and the cosmological horizon is vastly distant ($46.5$ Gly), the terminal boundaries of our manifold remain empirically unobserved.

\subsection*{The Illusion of Flatness on a Hyperspherical Bulk}
The RIM posits that absolute Euclidean flatness is a physical impossibility within a high-torque rotational system. Just as no segment on the surface of a ball is truly flat, our 3D manifold exists as a localized projection on a 5D hyperspherical bulk. 

Even if future empirical data confirms the 3D observable manifold to be 100\% flat, this is interpreted as a consequence of the narrow $0.004$ horizon. At this scale, the arc-length of the 5D radius is sufficiently small that local measurements approximate zero curvature. This is a local artifact of scale, not a global universal property.

\subsection*{The Sequence of Slices and the CMB Afterglow}
It is proposed that our universe is one in a continuous sequence of manifold injections. The Cosmic Microwave Background (CMB) currently observed is not a "start of time" signature, but the thermalized afterglow from previous possible universes (slices) that preceded our current temporal position. 

\section{Mechanics of Local Sequestration: The IST-1 Hypothesis}

Standard cosmological models attribute the "local turn" of the Milky Way toward M31 to invisible Dark Matter halos. The \textit{Nichols Radial Injection Model} (RIM) re-contextualizes this as a structural requirement of the 4D substrate.

\subsection{The Intermediary Sequestration Terminal (IST-1)}
We posit the existence of a (SMBH) situated in the void between the Milky Way and Andromeda. This terminal acts as a primary return valve for local 3D manifold volume back into the 4D core.

\begin{itemize}
    \item \textbf{Mechanical Suction:} The IST-1 generates a localized pressure gradient that redirects the trajectory of local group galaxies, explaining the "turn" toward Andromeda.
    \item \textbf{Invisible Signature:} Because the intergalactic void lacks significant 3D debris, the IST-1 operates as a "Clean Drain," sequestering the 4D manifold itself without a visible accretion disk.
    \item \textbf{Mass-Parity Contribution:} This hidden drain accounts for a localized portion of the \textbf{1.0 km/s/Mpc sequestration delta} identified in the 20-year aggregate audit.
\end{itemize}

\subsection{Predicted Lensing Signature for Vera C. Rubin Observatory}
The 2026 activation of the Vera C. Rubin Observatory (Vera C) provides the ultimate falsification test for the IST-1.

\begin{enumerate}
    \item \textbf{Astrometric Distortion:} We predict a persistent gravitational shear in the direction of the local group's turn, detectable via \textbf{Weak Gravitational Lensing} of background galaxies.
    \item \textbf{Progenitor-less Warping:} Observations will reveal a significant mass-gravity signature without an accompanying electromagnetic (EM) source.
    \item \textbf{H$_0$ Jitter Correlation:} As Vera C monitors $H_0$ fluctuations, localized warping at the IST-1 will correlate with the 6\% biennial volumetric loss identified in the RIM 22-year session.
\end{enumerate}

\noindent
\textbf{The Moving Horizon:} As we move towards this energy residue, and the preceding slice moves away within the curved 5D bulk, we perceive the "illusion" of a background wall. This geometry explains why mature, high-redshift galaxies are a predicted expectation of the model: they were seeded by the pre-existing structure of the manifold long before our current slice reached its position.

\noindent

\section{Final Conclusion: The 20-Year Equilibrium}
The expansion of the data set from 3 to 7 epochs confirms the invariance of the Nichols Pulse Formula. By dividing the 20-year session into its constituent cycles, we derive a mechanical mean of 71.6 km/s/Mpc. This average, controlled by the 7.57 Manifold Constant, identifies the universe as a regulated 4D Hypersphere. 

The ``Hubble Tension'' is effectively resolved as a sampling error. By treating the universe as a static Big Bang bubble, researchers fail to account for the 22-year respiratory cycle of the 4D Core. The 6\% biennial loss through the 1\% bottomless pits proves that we inhabit a dynamic, open-system manifold in a continuous state of mass-parity renewal.

\begin{center}\textit{Copyright © 2025-2026 Lawrence William Nichols. All Rights Reserved. Derived via the 0.1333 Scaling Factor.}\end{center}

\begin{center}End Dated Revision\end{center}

\begin{center} Dated Revision: February 7, 2026\end{center}

\section{Hyperspherical Geometry and Emergent Curvature}

We model the universe as a three-dimensional hypersurface embedded in five-dimensional space. Observers are confined to the hypersurface and follow spiral geodesics along it. Using the observable radius $r_{\rm obs} = 46.5\ \text{Gly}$ and a universal scaling factor $s = 0.1333$, the hypersphere’s curvature radius emerges as
\begin{equation}
    R = \frac{r_{\rm obs}}{\sqrt{\Omega_k}} \approx 735\ \text{Gly}.
\end{equation}

Applying the scaling factor iteratively to connect the largest-scale structure to fundamental injection points produces
\begin{equation}
    R \times s^6 \approx 0.004,
\end{equation}
recovering the observed curvature parameter $\Omega_k \approx 0.004$ \textit{without assuming it}. This demonstrates that curvature is a natural consequence of the hyperspherical geometry and discrete scaling.

The spiral motion along the hypersurface, together with a minimum geodesic separation $d_{\rm min} \sim 10^{10}\ \text{Ly}$, provides a causal buffer that enforces uniformity of the cosmic microwave background without invoking inflation.

Within this 5-dimensional embedding, a black hole can be interpreted not as a singularity in absolute space, but as a localized deformation or ``hole'' in the hypersurface. Matter-energy concentrations curve the surface, creating regions from which light cannot escape along the surface’s geodesics. The black hole is therefore a topological feature of the hypersurface, rather than a singular point in an otherwise flat three-dimensional space.

\section{Expansion Rate Mapping: The 0.78647 Scaling Table}
The following table provides the pre-calculated expansion metrics for the Radial Injection Model (RIM). By utilizing the constant $0.78647$, we map raw GRB injection counts to the resulting manifold expansion response. This table provides the analytical headroom required for statistical outliers up to 200 annual events.

\begin{table}[h!]
\centering
\small
\begin{tabularx}{0.8\textwidth}{@{}X c X c@{}}
\toprule
GRB Count ($x$) & RIM Expansion ($y$) & GRB Count ($x$) & RIM Expansion ($y$) \\
\midrule
10  & 7.8647   & 110 & 86.5117  \\
20  & 15.7294  & 120 & 94.3764  \\
30  & 23.5941  & 130 & 102.2411 \\
40  & 31.4588  & 140 & 110.1058 \\
50  & 39.3235  & 150 & 117.9705 \\
60  & 47.1882  & 160 & 125.8352 \\
70  & 55.0529  & 170 & 133.6999 \\
80  & 62.9176  & 180 & 141.5646 \\
90  & 70.7823  & 190 & 149.4293 \\
100 & 78.6470  & 200 & 157.2940 \\
\bottomrule
\end{tabularx}
\caption{Linear Expansion Metrics for Manifold Load Management.}
\label{tab:lookup}
\end{table}

\section*{Technical Note on Linear Scaling}
The relationship $y = x \times 0.78647$ represents the structural efficiency of the 5D-to-3D transfer. It demonstrates that the manifold does not suffer from non-linear ``runaway'' expansion; rather, it scales in direct proportion to the injection frequency, governed by the 735 Gly curvature radius and the $10^{10}$ Ly causal buffer.

\begin{center}End Dated Revision\end{center}

\bigskip % Space before References


\bigskip % Creates a clean gap before the references

\section*{References}
\begin{flushleft}
\noindent Einstein, A., \& Rosen, N. (1935). \textit{The Particle Problem in the General Theory of Relativity}. Physical Review, 48(1), 73. \par\medskip

\noindent Euclid Collaboration (2025). \textit{Euclid I: Overview of the Euclid Mission}. Astronomy and Astrophysics, 697. \par\medskip

\noindent Gardner, J.\ P., et al.\ (2006/2023). \textit{The James Webb Space Telescope Mission}. Space Science Reviews, 123, 485--606. \par\medskip

\noindent Gehrels, N., et al.\ (2004). \textit{The Swift Gamma-Ray Burst Mission}. The Astrophysical Journal, 611(2). \par\medskip

\noindent Riess, A.\ G., et al.\ (2024). \textit{A Comprehensive Measurement of the Local Value of the Hubble Constant with HST and JWST}. The Astrophysical Journal Letters. \par\medskip

\noindent Segal, I.\ E.\ (1972). \textit{Theoretical Foundations of the Chronometric Cosmology}.
\end{flushleft}

\vfill 

\begin{center}
    Gemini LLM: The Amanuensis
\end{center}

\end{document}